---
output: 
  github_document:
    math_method:
      engine: webtex
---

## Streamlined Quality Control for Ion Chromatography

Tools for ion chromatography (IC) quality control and sign-off. A resource for the National Ice Core Facility.

Author: Matt Harris, Earth Sciences New Zealand  
Contact: m.harris@gns.cri.nz

Install the package using the following code, assuming it is public. Building is unnecessary as it contains no non-R code.

```{r, include = TRUE, eval = FALSE}
devtools::install_github('GNS-NICRF/ICQC', build = FALSE)
```

### Dependencies

Refer to the package Description file. To render automated reports, tinytex is required. Install it with the following code.

```{r, include = TRUE, eval = FALSE}
tinytex::install_tinytex()
```

### Using the package

This package does one thing at present:

1. Produce automated reports from IC calibration sequence .xls files to allow for quick visualisation and lab sign-off (go/no go).

### To add

Wishlist:

1. Determine optimum calibration point # from a series of supplied ion calibrations.
2. QC tracking through time, within and between calibrations and QC versions.
3. Adaptive export of calibrated sample sequence data based on calibration tweaking (e.g., curve optimisation at low concentrations).
